\documentclass{article}

\begin{document}
\begin{center}
{\Large\bf By-laws of ``The GGobi Foundation''}
\end{center}

\date{}

\section{Name, Seat and Field of Activity}

\begin{enumerate} \itemsep 0in
\item The organization is named ``The GGobi Foundation''.
\item It is seated in Ames, Iowa and is active worldwide.
\end{enumerate}

\section{Objectives}

\begin{enumerate} \itemsep 0in
\item Fundamentals
\begin{enumerate} \itemsep 0in
\item The activities of the ``GGobi Foundation'' and its members are not 
influenced by politics or religion; people may become members
regardless of nationality, religion, or place of residency.
\item The ``GGobi Foundation'' is a non-profit organization working in the 
public interest.
\end{enumerate}
\item The objectives of the ``GGobi Foundation'' are:
\begin{enumerate} \itemsep 0in
\item Advance the GGobi project by designing, developing and
distributing free and open source software for interactive and dynamic
data visualization as part of data analysis.
\item Promote knowledge about and use of interactive and dynamic
graphics in data analysis.
\end{enumerate}
\end{enumerate}

\section{Means to Meet the Objectives}

\begin{enumerate} \itemsep 0in
\item To meet its objectives the organization will especially:
\begin{enumerate}
\item Support further development of GGobi and related open source graphics 
software projects.
\item Coordinate research projects, communicate with the user community,
and organize or sponsor courses.
\item Manage internet information systems like email and a web site.
\item Publish manuals and documentation related to using interactive and 
dynamic graphics.
\end{enumerate}
\item The material means of the organization to meet its objectives will come
from publishing royalties, profits from workshops, membership fees,
donations and contributions.
\end{enumerate}

\section{Membership}

\begin{enumerate} \itemsep 0in
\item The ``GGobi Foundation'' consists of ordinary and supporting
members.  Ordinary members have a vote in the general assembly and
participate actively in the work of the organization.  Supporting
members have no vote and promote the organization primarily by
paying membership fees.
\item Only natural persons can become ordinary members.  New ordinary
members shall be admitted only by majority vote of the existing
ordinary members.  The initial set of ordinary members will consist of
the active members of the GGobi development team at the inception of
the ``GGobi Foundation'': Deborah F. Swayne, Dianne Cook, Hadley
Wickham, Heike Hofmann, Michael Lawrence, Duncan Temple Lang, Andreas
Buja.
\item Any person or legal entity may become a supporting
member. Supporting members must be approved by majority vote of the
general assembly. Admission or approval for membership can be rejected
without public justification.
\item Membership terminates 
\begin{enumerate} \itemsep 0in
\item at the death of a person or the termination of existence of
legal entities.
\item by voluntary withdrawal from membership through written notice
to the board of directors.
\item by an affirmative vote of a two-thirds majority of the ordinary
members.
\end{enumerate}
\end{enumerate}

\section{General Assembly}

\begin{enumerate} \itemsep 0in
\item The ordinary members of the ``GGobi Foundation'' at a meeting
convened in the manner specified in paragraph \ref{meeting} or casting
their votes as described in paragraph \ref{vote} constitute the
general assembly, and are the highest authority of the ``GGobi
Foundation''. Each ordinary member shall have one vote in the general
assembly.

\item A meeting of the general assembly shall take place at least 
once every two years. A call, specifying the place, date, time and the
agenda will be sent to all ordinary members not less than a month
before the date of the meeting of the general assembly. This note can
be sent by written notice, fax or email (to the fax number or email
address specified by the member to the organization). The meeting
constitutes a quorum if at least two thirds of all ordinary members
are present or have sent a representative with written
authorization.\label{meeting}

\item A meeting of the general assembly shall be called upon request 
by two members of the board of directors or one quarter of all
ordinary members.

\item In addition to meetings of the general assembly, decisions can be 
reached by casting votes using mail, fax or email. Questions under
consideration must be sent to all ordinary members not less than one
month before the date by which replies have to reach the board of
directors. \label{vote}

\item All decisions of the general assembly are reached by majority 
vote unless otherwise stated in these by-laws.

\item The business transactions of the general assembly include:
\begin{enumerate} \itemsep 0in
\item Election and dismissal of members of the board.
\item Acceptance of activity report, statement and estimates of account.
\item Determination of membership fees.
\item Approval or rejection of changes to these by-laws.
\item Decision to terminate the ``GGobi Foundation''.
\item Discussion of and decisions on other topics of the agenda.
\end{enumerate}
\end{enumerate}

\section{Board of Directors}

\begin{enumerate} \itemsep 0in
\item The Board of Directors consists of at least three persons:

\begin{enumerate} \itemsep 0in
\item President
\item Secretary 
\item Treasurer
\end{enumerate}

\item All members of the Board are elected by the General Assembly for a
term of two years, with possible re-election. 
\item Decisions by the board are by majority vote.
\item The Board manages the business of the ``GGobi Foundation'' and
deals with all tasks not assigned to other ordinary members, especially:
\begin{enumerate} \itemsep 0in
\item Preparation of activity report, statement, and estimates of account.
\item Preparation of and call for general assemblies.
\item Management of all assets.
\end{enumerate}
\item The president represents the ``GGobi Foundation'' on official
occasions, presides over meetings and is responsible for the overall
direction of activities.
\item The secretary coordinates the activities of the organization,
supports the president in leading the organization, keeps records
of all general assemblies and decisions of the board, and keeps the
web site current.
\item The treasurer is responsible for the accounting and asset
management of the organization.
\item Written contracts of the ``GGobi Foundation'' have to be signed
by the president and secretary. Contracts concerning financial
transactions have to be signed by the president and
treasurer. Business transactions between members of the Board and the
``GGobi Foundation'' have to be approved by the general assembly.
\end{enumerate}

\section{Inspection of Records}

Books, accounts, documents and records of the orgnization will be open
to inspection by any director, or ordinary members, at all reasonable
times.

\section{Termination of Offices}

The office of a member of the board terminates by

\begin{enumerate} \itemsep 0in
\item death of the person, or end of term,
\item dismissal by a majority vote of the General Assembly,
\item voluntary withdrawal through written notice to the current board.
\end{enumerate}

\section{Termination}

The General Assembly shall have the right to decide to liquidate the
organization, by a majority vote. The Board of Directors will decide
on a recipient and who is to be responsible for the necessary
transactions. The recipient should be an organization with similar
goals to the GGobi Foundation, if possible and legal, or otherwise
charitable goals such as a scholarship fund.

\end{document}
